---
title: "loadshaper 1.1.1"
author: "Md Riaz Ahmed Khan"
output:
  md_document:
    variant: markdown_github
---



## R package loadshaper

The goal of this R package is to project a base 8760 (electric) load shape in order to match a target peak and target energy (or, energy via target load factor). Two methods were developed and implemented. Generics methods like `summary`, `print`, `plot` can be applied to certain objects. A score metric was developed and implemented to assess the output in terms of retaining general time series property. 

See [here](https://rpubs.com/riazakhan94/load_shape_match_peak_energy) for the description of the methods.


# Example

```{r}
library(loadshaper)
# base load shape
input_8760 <- ercot[ercot$Year == 2019, ]$ERCOT
pf_base <- mean(input_8760) / max(input_8760)
max_base <- max(input_8760)

message("Base Load Max:", max_base)
message("Base Load Power Factor:", pf_base)
```

# Project to Different Load Factor


## Higher Load Factor, Linear method
```{r}
y <- lslin(input_8760, target_max = max_base, target_lf = 0.65)
summary(y)

# Plot 
plot(y, case = 1)
plot(y, case = 2)

# Score
print(lscore(y, lag = 24))
```
## Higher Load Factor, Logistic method

```{r}
y <- lslog(input_8760, target_max = max_base, target_lf = 0.65,
           k = 0.5, inf_pos = 0.2)
summary(y)

# Plot 
plot(y, case = 1)
plot(y, case = 2)

# Score
print(lscore(y, lag = 24))
```

## Smaller Load Factor, Linear method
```{r}
y <- lslog(input_8760, target_max = max_base, target_lf = 0.45,
           k = 1, inf_pos = 0)
summary(y)

# Plot 
plot(y, case = 1)
plot(y, case = 2)

# Score
print(lscore(y, lag = 24))
```



## Smaller Load Factor, Logistic method
```{r}
y <- lslin(input_8760, target_max = max_base, target_lf = 0.45)
summary(y)

# Plot 
plot(y, case = 1)
plot(y, case = 2)

# Score
print(lscore(y, lag = 24))
```